Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 inspiral_svd.tex
Picked PACS numbers -- same as SVD paper
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@868 ccdd05d5-56c1-461a-bf98-85f6876523b4
Removed unused documentclass options
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@869 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added editorial note about author e-mails
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@870 ccdd05d5-56c1-461a-bf98-85f6876523b4
Author list conforms to guidelines: no full stops, last author separated by 'and'
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floo

\documentclass[showpacs,groupedaddress,showkeys,preprintnumbers]{iopart}
\input{packages}
\input{macros}
\renewcommand{\arraystretch}{1.2}

@@

\author{Kipp Cannon$^{1}$, Romain Cariou$^{2}$, Adrian Chapman$^3$, M.
Crispin-Ortuzar$^4$, Nickolas Fotopoulos$^3$, Melissa Frei $^5$, Chad
Hanna$^{6}$, Erin Kara$^{7}$, Drew Keppel$^{8,9}$, Laura Liao$^{10}$, Stephen
Privitera $^3$, Antony C.  Searle$^3$, Leo Singer$^3$, Alan J.  Weinstein$^3$}

\editorial{We have only Institution, City, State, Country for some co-authors.  Can we get rid of the full addresses, or is this at the discretion of the co-authors?}
\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, 61
Avenue du Pr\'{e}sident Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

@@

\pacs{95.55.Ym, 84.30.Vn, 95.75.Wx}

>>>>

\documentclass{iopart}
\input{packages}
\input{macros}
\renewcommand{\arraystretch}{1.2}

@@

\author{Kipp Cannon$^{1}$, Romain Cariou$^{2}$, Adrian Chapman$^3$, M
Crispin-Ortuzar$^4$, Nickolas Fotopoulos$^3$, Melissa Frei $^5$, Chad
Hanna$^{6}$, Erin Kara$^{7}$, Drew Keppel$^{8,9}$, Laura Liao$^{10}$, Stephen
Privitera $^3$, Antony C Searle$^3$, Leo Singer$^3$ and Alan J  Weinstein$^3$}

\editorial{We have only Institution, City, State, Country for some co-authors.  Can we get rid of the full addresses, or is this at the discretion of the co-authors?  How about author e-mails?}
\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, 61
Avenue du Pr\'{e}sident Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

@@

\pacs{04.30.-w, 07.05.Kf}
